Model Estimation

### 2018-12-07 model_estimation.Rmd
More edits to model optimization functions

## Model without Tweets

@@

  sdm <- lagsarlm(update(model, . ~ . + logsum), data = tracts@data, 
                  listw = W, zero.policy = TRUE, type = "mixed")
  return(-as.numeric(logLik(sdm)))
}

access_sdm_val <- optim(
  fn = notweets_logsum,  
  par = c(-1, 0), # distance, size 
  lower = c(-100, -100), # size coefficient must be positive 
  upper = c(0, 100), # distance coefficient must be negative 
  hessian=TRUE, distances = log(distances), parks = parks, tracts = tracts, 
  model = obese_base_lm, method = "L-BFGS-B", control = list(trace = 6))
```

@@

  estimation_data <- tracts@data %>% 
    mutate(logsum = calculate_park_logsums(
      d = distances,  sizes = parks$log_size,  tweets = parks$log_tweets,
      betas = betas))

  sdm <- lagsarlm(update(model, . ~ . + logsum, data = tracts@data), 
                  listw = W, zero.policy = TRUE, type = "mixed")

  return(-as.numeric(logLik(sdm)))
}

tweets_sdm_val <- optim(
  fn = notweets_logsum,  
  par = c(-1, 1, 0),
  lower = c(-100, 0, -100), # size coefficient must be positive
  upper = c(-1e-9, 100, 100), # distance coefficient must be negative
  hessian=TRUE, distances = distances, parks = parks, tracts = tracts, 
  model = obese_base_lm, method = "L-BFGS-B", control = list(trace = 6))

@@

```{r obesity_access_models}
tracts@data <- tracts@data %>%
  mutate(
    access_ls = calculate_park_logsums(distances, parks$log_size, 
                                       betas = notweets_lm_val$par),
    tweets_ls = calculate_park_logsums(distances, parks$log_size, parks$log_tweets, 
                                       betas = tweets_lm_val$par),
    # demean
    access_ls = access_ls - mean(access_ls),
    tweets_ls = tweets_ls - mean(tweets_ls)
  )

access_sdm <- lagsarlm(update(obese_base_sdm, .~ . + access_ls),   
                       data = tracts@data,  listw = W, zero.policy = TRUE, 
                       type = "mixed")
tweets_sdm <- lagsarlm(update(obese_base_sdm, .~ . + tweets_ls),   
                       data = tracts@data,  listw = W, zero.policy = TRUE, 
                       type = "mixed")
```

@@

```{r physact_estimation}
pa_base_sdm <- lagsarlm(update(base_formula, PHYSACT ~ .),
         data = tracts@data,  listw = W, zero.policy = TRUE, type = "mixed")
pa_access_sdm <- lagsarlm(update(base_formula, PHYSACT ~ . + notweets_ls),  
          data = tracts@data,  listw = W, zero.policy = TRUE, type = "mixed")
pa_tweets_sdm <- lagsarlm(update(base_formula, PHYSACT ~ . + tweets_ls),  
          data = tracts@data,  listw = W, zero.policy = TRUE, type = "mixed")
```

```{r physact_models}
physact_models <- list(Base = pa_base_sdm, Access = pa_notweets_sdm, 
                       `Access + Tweets` = pa_tweets_sdm)
screenreg(physact_models, digits = 4)
```

@@

```{r logsum_scales}
data_frame(
  Parameter = c("Distance", "Size", "Tweets"),
  Access = c(notweets_lm_val$par, NA),
  `Access + Tweets` = tweets_lm_val$par
)

>>>>

@@

  tracts@data$logsum <- logsum

  sdm <- update(model, . ~ . + logsum)

  return(logLik(sdm))
}

access_sdm_val <- optim(
  fn = notweets_logsum,  
  par = c(-1, 2), # distance, size 
  lower = c(-100, 0), # size coefficient must be positive 
  upper = c(0, 100), # distance coefficient must be negative 
  distances = log(distances), parks = parks, tracts = tracts, 
  model = obese_base_sdm, 
  method = "L-BFGS-B", 
  control = list(fnscale = -1, trace = 6))
```

@@

  logsum <- calculate_park_logsums(
    d = distances,  sizes = parks$log_size, tweets = parks$log_tweets,
    betas = betas)

  tracts@data$logsum <- logsum
  sdm <- update(model, . ~ . + logsum)

  return(logLik(sdm))
}

tweets_sdm_val <- optim(
  fn = notweets_logsum,  
  par = c(-1, 1, 0),
  lower = c(-100, 0, -100), # size coefficient must be positive
  upper = c(0, 100, 100), # distance coefficient must be negative
  hessian=TRUE, distances = distances, parks = parks, tracts = tracts, 
  model = obese_base_sdm, 
  method = "L-BFGS-B", 
  control = list(fnscale = -1, trace = 6))

@@

```{r obesity_access_models}
tracts@data <- tracts@data %>%
  mutate(
    access_ls = calculate_park_logsums(log(distances), parks$log_size,
                                       betas = access_sdm_val$par),
    tweets_ls = calculate_park_logsums(log(distances), parks$log_size, parks$log_tweets,
                                       betas = tweets_sdm_val$par),
    # demean
    access_ls = access_ls - mean(access_ls),
    tweets_ls = tweets_ls - mean(tweets_ls)
  )

access_sdm <- update(obese_base_sdm, .~ . + access_ls)
tweets_sdm <- update(obese_base_sdm, .~ . + tweets_ls)
```

@@

```{r physact_estimation}
pa_base_sdm <- update(obese_base_sdm, log_physact ~ .)
pa_access_sdm <- update(access_sdm, log_physact ~ .)
pa_tweets_sdm <- update(tweets_sdm, log_physact ~ .)
```

```{r physact_models}
physact_models <- list(Base = pa_base_sdm, Access = pa_access_sdm, 
                       `Access + Tweets` = pa_tweets_sdm)
screenreg(physact_models, digits = 4)
```

@@

```{r logsum_scales}
data_frame(
  Parameter = c("Distance", "Size", "Tweets"),
  Access = c(access_sdm_val$par, NA),
  `Access + Tweets` = tweets_sdm_val$par
)
